---
date-format: "YYYY-MM-DD hh:mm:ssa z"
date: now
published-title: "Report Created"
params:
  # A value that can be `S7::convert`'ed into a `val.meter::pkg`
  # 
  # Common inputs include:
  #
  #   - DESCRIPTION (or PACKAGES) file string
  #   - PACKAGES file string
  #   - a package name (to be sourced from a repository)
  #   - a list of package metadata and metrics
  #   - an Rds file generated from a val.meter::pkg object
  #
  package: NULL
  
  # Additional options to set during evaluation.
  #
  # These may be especially useful if the report is used for performing package
  # evaluations, in which case you may consider passing `?val.meter::options` to
  # enable addition evaluation permissions.
  #
  # To set options using R code, pass a string prefixed with "!expr".
  #
  options: NULL
  
  # Session info to attach to the report
  #
  # When empty, defaults to `val.report::session()` captured during report
  # generation. If you wish to provide information captured from previous
  # execution, provide `val.report::session()` from that session as a parameter,
  # either as an R object or a `.Rds` file path.
  #
  session: NULL
  
  image: "rocker/rver"
  hide_reverse_deps: true

format:
  r-val-hub-report-html: default
  r-val-hub-report-typst:
    keep-typ: true
---

```{r setup, include = FALSE}
options(
  width = 80L, 
  covr.record_tests = TRUE,
  crayon.enabled = TRUE,
  cli.ansi = TRUE,
  # if calculated in report, keep logs
  val.meter.logs = TRUE
)

knitr::opts_chunk$set(
  echo = FALSE,
  eval = TRUE,
  error = TRUE,
  cache = FALSE
)

library(S7)
library(tools)
library(knitr)
library(val.meter)
library(val.report)

format <- knitr::opts_knit$get("rmarkdown.pandoc.to") %||%
  knitr::opts_knit$get("out.format")

callout <- switch(
  format,
  "typst" = "",
  '.callout appearance="minimal" collapse="true"'
)

header <- val.report::knitr_mutable_header()
log <- val.report::knitr_logger()
```

```{r loading, include = FALSE}
if (is.null(params$package)) {
  stop(
    "The `package` parameter is required. At a minimum pass a package ",
    "name, which will be discovered from installed packages or sourced from a ",
    "repository. For details, see `?val.report::report()`."
  )
}

# parse options, handling expression strings
opts <- val.report::knitr_update_options(params$options)
log("parsed `params$options` as:\n", opts, "\n\n")

# parse provided parameter session info or default to current session
session <- params$session
log("session `params$session` as:\n", session, "\n\n")
log(file.exists(session))
if (is.character(session) && file.exists(session) && endsWith(session, ".Rds")) {
  session <- readRDS(session)  
}

log(
  "using ", if (is.null(params$session)) "current" else "param", 
  " session captured at: ", format(as.POSIXct(session$time)), "\n\n"
)

# derive a package object from parameter value
pkg <- convert(params$package, val.meter::pkg)
log("parsed `params$package` into val.meter::pkg from:\n", pkg@resource, "\n\n")

# calculate package metrics
met <- metrics(pkg)
log("evaluated metrics:\n", met, "\n\n")

header$title <- paste0("`", pkg$name, "` v", pkg$version)
```

# Methodology

The following metrics are derived from the `val.meter` R package. `val.meter`
is built by the [R Validation Hub](https://www.pharmar.org), a
cross-industry working group operating under the
[R Consortium](https://www.r-consortium.org), and is designed to consistently
and reproducibly evaluate packages.

# Results

## Standard Checks

::: {.grid}
{{< typst-grid-start >}}

```{r, include = FALSE}
metric <- pkg_data_info("r_cmd_check_error_count")
value <- pkg$r_cmd_check_error_count
style <- if (value > 0) "danger" else "success"
```

{{<
  metric-card
  span=4
  style=`r style`
  title=Errors
  footer='`r capture.output(tools::Rd2HTML(metric@description, fragment = TRUE))`'
  text='`r pkg$r_cmd_check_error_count`'
>}}

```{r, include = FALSE}
value <- length(pkg$r_cmd_check$warnings)
style <- if (value > 0) "warning" else "success"
```

{{<
  metric-card
  span=4
  style=`r style`
  title=Warnings
  footer='number of warnings produced by <code>R CMD check</code>'
  text='`r value`'
>}}

```{r, include = FALSE}
value <- length(pkg$r_cmd_check$notes)
style <- if (value > 0) "warning" else "success"
```

{{<
  metric-card
  span=4
  style=`r style`
  title=Notes
  footer='number of notes produced by <code>R CMD check</code>'
  text='`r value`'
>}}

{{< typst-grid-end >}}
:::

::: {`r callout` title="<code>R CMD check</code> logs"}
```{r rcmd_check_logs_setup, include=FALSE}
library(rcmdcheck)
has_results <- !is.null(pkg$r_cmd_check) && !inherits(pkg$r_cmd_check, "error")
has_logs <- !is.null(pkg@logs$r_cmd_check)
```
```{r r_cmd_check_exec_logs, include=has_logs}
library(rcmdcheck)
pkg@logs$r_cmd_check
```
```{r r_cmd_check_results_logs, include=has_results}
cat(val.meter::format_output(pkg$r_cmd_check))
```
:::

## Good Practices

::: {.grid}
{{< typst-grid-start >}}

```{r, include = FALSE}
metric <- pkg_data_info("test_line_coverage_fraction")
value <- pkg$test_line_coverage_fraction
style <- if (value > 0.6) "success" else if (value > 0.2) "warning" else "danger"
```

{{<
  metric-card
  span=4
  style=`r style`
  title='Code Coverage'
  footer='`r metric@description`'
  text='`r sprintf("%.1f%%", value * 100)`'
>}}

{{<
  metric-card
  span=4
  title='Documentation Coverage'
  footer='percentage of exported package objects that have corresponding documentation'
  text='TODO'
>}}

{{<
  metric-card
  span=4
  title='Public Website'
  footer='whether the package lists a website associated with the project'
  text='TODO'
>}}

{{<
  metric-card
  span=4
  title='Public Bug Reports'
  footer='whether the package provides a pathway for submitting bug reports'
  text='TODO'
>}}

{{< typst-grid-end >}}
:::

::: {`r callout` title="<code>covr::package_coverage()</code> summary"}
```{r covr_coverage_summary}
library(covr)
cat(val.meter::format_output(pkg$covr_coverage))
```
:::

## Adoption

# Evaluation Environment

## System Information

```{r execution_info}
#| tab.cap: "System characteristics measured when evaluating the package"

tt_sys_info_df <- data.frame(
  Field = c("OS", "Platform", "System", "R Version", "Execution Time"),
  Value = c(
    session$session_info$running,
    session$r_version$platform,
    session$r_version$system,
    session$r_version$version.string,
    format(as.POSIXct(session$time), tz = "UTC", usetz = TRUE)
  )
)

knitr::kable(tt_sys_info_df)
```

::: {`r callout` title="Comprehensive R Session Information"}
## Generic Session Information

```{.r}
sessionInfo()
```
```{r}
session$session_info
```

## Platform Details

```{.r}
.Platform
```
```{r}
unlist(session$platform)
```

## System Capabilities

```{.r}
capabilities()
```
```{r}
unlist(session$capabilities)
```

## Relevant External Software Installed

```{.r}
extSoftVersion()
```
```{r}
unlist(session$external_software)
```

## Relevant Graphics Software Installed

```{.r}
grSoftVersion()
```
```{r}
unlist(session$graphics_software)
```

## Machine Details

```{.r}
.Machine
```
```{r}
unlist(session$machine)
```

## Random Number Generator Capabilities

```{.r}
RNGkind()
```
```{r}
session$rng_kind
```

## Environment Variables Set During Evaluation

Environment variables and R options affect how package checks and software in it
might behave.

```{r environment_variables}
val.report::environ_report(
  exclude = c(
    "APPDATA", "GITHUB", "GITHUB_PAT", "GITHUB_PAT_GITHUB_COM", 
    "GITLAB", "GITLAB_PAT", "ProgramFiles", "ProgramFiles(x86)", 
    "R_DptShare", "R_USER", "USERDNSDOMAIN", "USERDOMAIN",
    "USERDOMAIN_ROAMINGPROFILE", "USERNAME", "USERPROFILE"
  )
)
```

## Options Set During Evaluation

```{r options}
val.report::options_report(exclude = c("usethis.full_name", "usethis.description", "usethis.destdir"))
```
:::
